---
title: "My Movies"
author: "João Neto"
date: "2021--2023"
output: 
  html_document:
    includes:
      in_header: header.html
---

<!--  To run shiny server place this above
runtime: shiny 
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(dplyr)
library(magrittr)
```
```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
movie.emote    <- utf8::utf8_print('\U0001F3A5')
director.emote <- utf8::utf8_print('\U0001F3AC')
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
df <- read.csv2('best_movies_info.csv', encoding='UTF-8')
df$Score <- as.numeric(df$Score)

# df$link <- paste0('<a href="https://www.imdb.com/title/', df$IMDB, '" target="_blank">imdb</a>')

# df$link.director <- paste0('<a href="https://www.imdb.com/filmosearch/?role=',df$directors,'&ref_=filmo_ref_job_typ&mode=detail&page=1&title_type=movie&sort=moviemeter,asc&job_type=director" target="_blank">',df$primaryName,'</a>')

df$links <- paste0('<a href="https://www.imdb.com/title/', df$IMDB, '" target="_blank">',movie.emote,'</a><a href="https://www.imdb.com/filmosearch/?role=',df$directors,'&ref_=filmo_ref_job_typ&mode=detail&page=1&title_type=movie&sort=moviemeter,asc&job_type=director" target="_blank">',director.emote,'</a>')

df %>% 
  rename(Rate = Score) %>% 
  rename(Director = primaryName) %>% 
  select(-directors) ->df 

### read imdb table

## we'll get imdb rate, movie time and popular votes from IMDB database

df.imdb <- read.csv('ratings.csv', encoding='UTF-8')
df.imdb %>% 
  rename(IMDB = Const) %>% 
  rename(Time = "Runtime..mins.") %>% 
  rename(Imdb = IMDb.Rating) %>% 
  rename(Votes = Num.Votes) %>% 
  select(-Your.Rating) %>% 
  select(-Date.Rated) %>% 
  select(-Title) %>% 
  select(-URL) %>% 
  select(-Genres) %>% 
  select(-Year) %>% 
  select(-Release.Date) %>% 
  select(-Directors) %>% 
  select(-Title.Type) -> df.imdb2

toDecade <- function(year) {
  if (year < 1920) {
    return("1910s")
  } else if (year < 1930) {
    return("1920s")
  } else if (year < 1940) {
    return("1930s")
  } else if (year < 1950) {
    return("1940s")
  } else if (year < 1960) {
    return("1950s")
  } else if (year < 1970) {
    return("1960s")
  } else if (year < 1980) {
    return("1970s")
  } else if (year < 1990) {
    return("1980s")
  } else if (year < 2000) {
    return("1990s")
  } else if (year < 2010) {
    return("2000s")
  } else if (year < 2020) {
    return("2010s")
  } else if (year < 2030) {
    return("2020s")
  } else if (year < 2040) {
    return("2030s")
  }
}

df$Decade <- sapply(df$Year, toDecade)

### Join Tables

df.join <- left_join(df, df.imdb2, by=c("IMDB"="IMDB"))
df.join %>% 
  select(-IMDB) %>% 
  select(Title,Year,Decade,Country,Genre,Time,Rate,Imdb,Votes,Director,links) -> df
```

This table includes movies I think have a higher than average quality in either plot, main themes and overall cinematography. I'll keep inserting recent movies at the top of the table, and older movies at the end of the table.

This list represents `r 100 * round(nrow(df) / nrow(df.imdb),3)`% of [all movies I've seen](https://www.imdb.com/user/ur3443219/ratings?ref_=nv_usr_rt_4) and is, obviously, quite subjective :-)

```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(DT)
DT::datatable(df, escape=FALSE) 
```

## Number of Selected Movies per Year

```{r, echo=FALSE}
min.score <- 7
my.color <- 'steelblue'
```

Showing movies with a minimal rating of `r min.score` (blue) and the rest (orange). The list of movies I want to see from 1960-1974 and from 2000-2022 is (somewhat) complete. My current goal is to do the same from the remaining 1970s to the end of the 1990s. *Then* I will move to the 1950s.

```{r, fig.width=12, echo=FALSE, eval=TRUE}
df %>% 
  filter(Rate >= min.score) %>% 
  count(Year, sort=TRUE) %>% 
  filter(Year >= 1960) %>%
  filter(Year < 1990) %>%
  arrange( Year ) -> df2

df.imdb %>% 
  count(Year) %>% 
  filter(Year >= 1960) %>%
  filter(Year < 1990) %>%
  arrange(Year) -> df2.imdb

data <- matrix(c(df2$n, df2.imdb$n-df2$n), nrow=2, byrow=TRUE)
#data <- matrix(c(df2$n), nrow=1)

par(mar=c(3,1,1,1))
#plt <- barplot(df2$n, names.arg=df2$Year, las=2, col=my.color,
#ylim=c(0,max(df2$n)*1.25), yaxt="n")

plt <- barplot(data, names.arg=df2$Year, las=2, col=c(my.color, 'orange'),
 ylim=c(0,100), yaxt="n")

text(x=plt, y=df2$n,      label=df2$n,      pos=3, cex=0.8, col='blue')
text(x=plt, y=df2.imdb$n, label=df2.imdb$n, pos=3, cex=0.8, col='blue')
```

```{r, fig.width=12, echo=FALSE, eval=TRUE}
df %>% 
  filter(Rate >= min.score) %>% 
  count(Year, sort=TRUE) %>% 
  filter(Year >= 1990) %>%
  arrange( Year ) -> df2

df.imdb %>% 
  count(Year) %>% 
  filter(Year >= 1990) %>%
  arrange(Year) -> df2.imdb

data <- matrix(c(df2$n, df2.imdb$n-df2$n), nrow=2, byrow=TRUE)
#data <- matrix(c(df2$n), nrow=1)

par(mar=c(3,1,1,1))
#plt <- barplot(df2$n, names.arg=df2$Year, las=2, col=my.color,
#ylim=c(0,max(df2$n)*1.25), yaxt="n")

plt <- barplot(data, names.arg=df2$Year, las=2, col=c(my.color, 'orange'),
 ylim=c(0,115), yaxt="n")

text(x=plt, y=df2$n,      label=df2$n,      pos=3, cex=0.8, col='blue')
text(x=plt, y=df2.imdb$n, label=df2.imdb$n, pos=3, cex=0.8, col='blue')
```


There are hundreds still to see from the 1920s to the 1950s, and these are the respective wish-lists:

+ [wishlist from the 1920s](https://www.imdb.com/list/ls088146253/?pf_rd_m=A2FGELUUNOQJNL&pf_rd_p=4dc7ad1a-76a6-49eb-9acb-5d6959572df8&pf_rd_r=2N4WWMA2RBEP12AVJGS9&pf_rd_s=right-4&pf_rd_t=48201&pf_rd_i=watchlist&ref_=wt_otl_1)

+ [wishlist from the 1930s](https://www.imdb.com/list/ls088107424/?pf_rd_m=A2FGELUUNOQJNL&pf_rd_p=4dc7ad1a-76a6-49eb-9acb-5d6959572df8&pf_rd_r=GJR77FD60TS77BB3BTM4&pf_rd_s=right-4&pf_rd_t=48201&pf_rd_i=watchlist&ref_=wt_otl_2)

+ [wishlist from the 1940s](https://www.imdb.com/list/ls088795556/?pf_rd_m=A2FGELUUNOQJNL&pf_rd_p=4dc7ad1a-76a6-49eb-9acb-5d6959572df8&pf_rd_r=0FCARTR5AZ8DRVB27SH3&pf_rd_s=right-4&pf_rd_t=48201&pf_rd_i=watchlist&ref_=wt_otl_4)

+ [wishlist from the 1950s](https://www.imdb.com/list/ls089830524/?pf_rd_m=A2FGELUUNOQJNL&pf_rd_p=4dc7ad1a-76a6-49eb-9acb-5d6959572df8&pf_rd_r=G8MGE7R65T5SR6M8362N&pf_rd_s=right-4&pf_rd_t=48201&pf_rd_i=watchlist&ref_=ttls_vw_grd&sort=list_order,asc&st_dt=&mode=grid&page=1)



```{r, echo=FALSE, eval=FALSE}
inputPanel(
  sliderInput("score", label="minimum movie score", 
              min=7, max=10, value=7.5, step=0.25)
)

output$g1 <- renderPlot({
  df %>% 
  filter(Rate >= input$score) %>% 
  count(Year, sort=TRUE) %>% 
  arrange( Year ) -> df2

  par(mar=c(3,1,1,1))
  plt <- barplot(df2$n, names.arg=df2$Year, las=2, col=my.color,
                 ylim=c(0,max(df2$n)*1.25), yaxt="n")
  text(x=plt, y=df2$n, label=df2$n, pos=3, cex=0.8, col='blue')
})

plotOutput("g1", height="400px")
br()
```


```{r, echo=FALSE, eval=TRUE}
rotate_x <- function(data, column_to_plot, labels_vec, rot_angle) {
  ymax <- max(data[[column_to_plot]])*1.25
  plt <- barplot(data[[column_to_plot]], col='steelblue', xaxt="n", yaxt="n", ylim=c(0,ymax))
  text(plt, par("usr")[3], labels = labels_vec, srt = rot_angle, 
       adj = c(1.1,1.1), xpd = TRUE, cex=1) 
  text(x = plt, y = data$n, label = data$n, pos = 3, cex = 1.2, col = my.color)
}
```

## Total ranked movies

These numbers include all movies I ranked at IMDB:

```{r, fig.width=6, fig.height=3, echo=FALSE, eval=TRUE}
df.imdb %>% 
  mutate(Decade = floor(Year/10)*10) %>% 
  count(Decade) %>% 
  arrange(Decade) -> df2

par(mar = c(2.5, .5, .5, .5))
rotate_x(df2, 'n', df2$Decade, 45)
```

## Number of Selected Movies per Decade

Number of movies with a score of at least 7:

```{r, fig.width=6, fig.height=3, echo=FALSE, eval=TRUE}
df %>% 
  filter(Rate >= min.score) %>% 
  count(Decade, sort=TRUE) %>% 
  arrange( Decade ) -> df2

par(mar = c(2.5, .5, .5, .5))
rotate_x(df2, 'n', df2$Decade, 45)
# plt <- barplot(df2$n, names.arg=df2$Decade, las=1, col=my.color, ylim=c(0,max(df2$n)*1.25), yaxt="n")
# text(x=plt, y=df2$n+0.8, label=df2$n, pos=3, cex=1, col=my.color)
```

```{r, echo=FALSE, eval=FALSE}
inputPanel(
  sliderInput("score2", label="minimum movie score", 
              min=7, max=10, value=7.5, step=0.25)
)

output$g2 <- renderPlot({
df %>% 
  filter(Rate >= input$score2) %>% 
  count(Decade, sort=TRUE) %>% 
  arrange( Decade ) -> df2

  plt <- barplot(df2$n, names.arg=df2$Decade, las=1, col=my.color,
                 ylim=c(0,max(df2$n)*1.25), yaxt="n")
  text(x=plt, y=df2$n+0.8, label=df2$n, pos=3, cex=1, col='blue')
})

plotOutput("g2", height="400px")
br()
```

## Movie quality per Decade

Let's see how many very good films (rating at least 8) each decade produced,

```{r, fig.width=6, fig.height=3, echo=FALSE}
df %>% 
  filter(Rate >= 8) %>% 
  count(Decade, sort=TRUE) %>% 
  arrange( Decade ) -> df2

par(mar = c(2.5, .5, .5, .5))
rotate_x(df2, 'n', df2$Decade, 45)
```

And how many great films (rating at least 9) per decade,

```{r, fig.width=6, fig.height=3, echo=FALSE}
df %>% 
  filter(Rate >= 9) %>% 
  count(Decade, sort=TRUE) %>% 
  arrange( Decade ) -> df2

par(mar = c(2.5, .5, .5, .5))
rotate_x(df2, 'n', df2$Decade, 45)
```

And masterpieces (rating of at least 9.5) per decade,

```{r, fig.width=6, fig.height=3, echo=FALSE}
df %>% 
  filter(Rate >= 9.5) %>% 
  count(Decade, sort=TRUE) %>% 
  arrange( Decade ) -> df2

par(mar = c(2.5, .5, .5, .5))
rotate_x(df2, 'n', df2$Decade, 45)
```

The next plot shows how different rating ranges are represented by decade,

```{r, fig.width=8, fig.height=6, warning=FALSE, echo=FALSE, message=FALSE}
df %>% 
  mutate(interval = cut(df$Rate, breaks=c(6.9,7.4,7.9,8.4,8.9,9.4,10))) %>% 
  group_by(Decade, interval, .drop = FALSE) %>% 
  summarise(count=n(), .groups = 'drop') -> df3

mat <- matrix(df3$count, ncol=6, byrow=T)

library(RColorBrewer)
par(mar = c(2.5, 2.5, 1.5, 1.5))
# https://www.datanovia.com/en/blog/the-a-z-of-rcolorbrewer-palette/
barplot(mat %>% t, names.arg=unique(df3$Decade), ylim=c(0,600), col=brewer.pal(6, "Blues") )
legend(.25, 400, rev(c('7+','7.5+','8+','8.5+','9+','9.5+')), 
       col=rev(brewer.pal(7, "Blues")), pch=15)
```

## Movies per Directors

Let's check directors with multiple movies in the list,

```{r, fig.width=14, fig.height=12, echo=FALSE}
df %>% 
  count(Director, sort=TRUE) %>% 
  filter(!is.na(Director)) %>% 
  filter(n>7) -> df4

par(mar=c(1,11,1,6))
plt <- barplot(df4$n, col='steelblue', horiz=TRUE, names.arg=df4$Director, 
               las=1, xlim=c(0,10+max(df4$n)), xaxt='n')
text(y=plt, x=df4$n+0.8, label=df4$n, pos = 2, cex = 0.8, col='blue')
```

Directors with movies with a rating of at least 8.5,

```{r, fig.width=14, fig.height=10, echo=FALSE}
df %>% 
  filter(Rate >= 8.5) %>% 
  count(Director, sort=TRUE) %>% 
  filter(!is.na(Director)) %>% 
  filter(n>2) -> df5

par(mar=c(1,11,1,1))
plt <- barplot(df5$n, col='steelblue', horiz=TRUE, names.arg=df5$Director, 
               las=1, xlim=c(0,10+max(df5$n)), xaxt='n')
text(y=plt, x=df5$n+0.4, label=df5$n, pos = 2, cex = 0.8, col='blue')
```

And, finally, who made the masterpieces (≥9.5),

```{r, fig.width=14, fig.height=10, echo=FALSE}
df %>% 
  filter(Rate >= 9.5) %>% 
  count(Director, sort=TRUE) %>% 
  filter(!is.na(Director)) -> df5

par(mar=c(1,11,1,1))
plt <- barplot(df5$n, col='steelblue', horiz=TRUE, names.arg=df5$Director, 
               las=1, xlim=c(0,10+max(df5$n)), xaxt='n')
text(y=plt, x=df5$n+0.4, label=df5$n, pos = 2, cex = 0.8, col='blue')
```

The next table sums, for each director, the scores of each film rated here. A film ranked 7 gets 1 point, 7.25 gets 2 points, upto a score 10 that gets 13 points. For the Imdb score, films with score less or equal to 6.5 get negative points.

```{r, echo=FALSE}
# a 7 receives 1 point, a 10 receives 13 points
score <- function(rate) {
  rate*4-27
}

director.score <- function(rates) {
  round(sum(as.numeric(Map(score, rates))),2)
}

df %>% 
  group_by(Director) %>% 
  summarize(Score = director.score(Rate)) -> directors

df %>% 
  group_by(Director) %>% 
  summarize(Score.Imdb = director.score(Imdb)) -> directors2

directors$Imdb <- directors2$Score.Imdb

directors %>% 
  arrange(desc(Score)) -> directors

DT::datatable(directors, escape=FALSE) 
```
The next table show these scores per decade and director.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
df %>% 
  group_by(Director, Decade) %>% 
  summarize(Score = director.score(Rate)) -> directors

df %>% 
  group_by(Director, Decade) %>% 
  summarize(Score.Imdb = director.score(Imdb)) -> directors2

directors$Imdb <- directors2$Score.Imdb

directors %>% 
  arrange(desc(Score)) -> directors

DT::datatable(directors, escape=FALSE) 
```

## Movies per Genre

The most represented genre is drama, an umbrella category for many different types of movie. The remaining genres are:

```{r, fig.width=10, fig.height=4, echo=FALSE}
df %>% 
  #filter(Score >= min.score) %>% 
  filter (Genre!='Drama') %>% 
  count(Genre) %>% 
  arrange( desc(Genre) ) -> df6

par(mar=c(1,11,1,1))
plt <- barplot(df6$n, col='steelblue', horiz=TRUE, names.arg=df6$Genre, 
               las=1, xlim=c(0,20+max(df6$n)), xaxt='n')
text(y=plt, x=df6$n+12, label=df6$n, pos=2, cex=0.8, col='blue')
```

## Movies per Country

```{r, warning=FALSE, echo=FALSE}
df %>% 
  filter(Rate >= 7) %>% 
  filter (Country=='USA') -> df.us
```

Hollywood is highly represented with a current total of `r nrow(df.us)` American movies. Let's check how other countries are represented:

```{r, fig.width=14, fig.height=12, warning=FALSE, echo=FALSE}
df %>% 
  filter(Rate >= 7) %>% 
  filter (Country!='USA') %>% 
  count(Country, sort=TRUE) %>% 
  arrange( desc(Country) ) -> df2

par(mar=c(1,11,1,6))
plt <- barplot(df2$n, col='steelblue', horiz=TRUE, names.arg=df2$Country,
               las=1, xlim=c(0,16+max(df2$n)), xaxt='n')
text(y=plt, x=df2$n+6.5, label=df2$n, pos = 2, cex = 0.8, col='blue')
```

## All rated movies on Imdb

This table includes all movies I rated on Imdb, including those with less than a rate of 7. On imdb the only allowed rates are integers from 1 to 10.

```{r, echo=FALSE, warning=FALSE}
df.imdb %>% 
  rename(Rate = Your.Rating) %>% 
  rename(Imdb = IMDb.Rating) %>% 
  rename(Votes = Num.Votes) %>% 
  rename(Time = Runtime..mins.) %>% 
  rename(Date = Release.Date) %>% 
  select(-Const) %>% 
  select(-URL) %>% 
  select(-Title.Type) %>% 
  select(-Date.Rated) %>% 
  select(Title,Date,Genres,Time,Directors,Rate,Imdb,Votes) -> df.imdb3

df.imdb3$link <- paste0('<a href="', df.imdb$URL, '" target="_blank">',movie.emote,'</a>')

DT::datatable(df.imdb3, escape=FALSE) 
```



```{r, fig.width=12, fig.height=10, echo=FALSE, eval=FALSE}
df %>% 
  filter(Rate >= 9) %>% 
  count(Country, sort=TRUE)  -> df2

par(mar=c(1,11,1,6))
plt <- barplot(df2$n, col='steelblue', horiz=TRUE, names.arg=df2$Country, 
               las=1, xlim=c(0,10+max(df2$n)), xaxt='n')
text(y=plt, x=df2$n+4, label=df2$n, pos = 2, cex = 0.8, col='blue')
```



```{r, echo=FALSE, eval=FALSE}
plot(df$Year, df$Rate, pch=20, col='lightgrey')
fit <- lm(Rate ~ Year, df)
abline(fit, col='blue')
```




