---
title: "My Movies"
author: "João Neto"
date: "28/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, warning=FALSE, message=FALSE}
library(dplyr)
library(magrittr)
```


```{r}
df <- read.csv2('best_movies_info.csv', encoding='UTF-8')
df$Score <- as.numeric(df$Score)
df %>% 
  rename(ImdbRate = averageRating) %>% 
  rename(Votes = numVotes) %>% 
  rename(Director = primaryName) %>% 
  select(-directors) %>% 
  select(-IMDB) -> df
```

```{r, warning=FALSE, echo=FALSE}
library(DT)
DT::datatable(df)
```



## Number of Selected Movies per Year

```{r}
min.score <- 7.5
my.color <- 'steelblue'
```

Only showing movies with a minimal score, given that more recent years have more lower score movies (I see more modern movies than old movies). And still have *lots* of movies to see from the 70s and 60s.

```{r, fig.width=12}
df %>% 
  filter(Score >= min.score) %>% 
  count(Year, sort=TRUE) %>% 
  arrange( Year ) -> df2
barplot(df2$n, names.arg=df2$Year, las=2, col=my.color)
```

## Number of Selected Movies per Decade

Again using the same filter as above:

```{r}
df %>% 
  filter(Score >= min.score) %>% 
  count(Decade, sort=TRUE) %>% 
  arrange( Decade ) -> df2
barplot(df2$n, names.arg=df2$Decade, las=1, col=my.color)
```

## Number of Selected Movies per Country

Most movies I see are from Hollywood, but let's check how others countries are represented:

```{r, fig.width=12, warning=FALSE}
rotate_x <- function(data, column_to_plot, labels_vec, rot_angle) {
  ymax <- max(data[[column_to_plot]])*1.25
  plt <- barplot(data[[column_to_plot]], col='steelblue', xaxt="n", ylim=c(0,ymax))
  text(plt, par("usr")[3], labels = labels_vec, srt = rot_angle, 
       adj = c(1.1,1.1), xpd = TRUE, cex=1) 
  text(x = plt, y = data$n, label = data$n, pos = 3, cex = 1.2, col = my.color)
}

df %>% 
  filter(Score >= min.score) %>% 
  filter (Country!='USA') %>% 
  count(Country, sort=TRUE) %>% 
  arrange( Country ) -> df2

rotate_x(df2, 'n', df2$Country, 45)
```

## Masterpieces per Decade

Herein I define as a masterpiece a movie with score at least 9.5.

```{r}
df %>% 
  filter(Score >= 9.5) %>% 
  count(Decade, sort=TRUE) %>% 
  arrange( Decade ) -> df2

rotate_x(df2, 'n', df2$Decade, 45)
```

```{r, fig.width=10, warning=FALSE}
df %>% 
  mutate(interval = cut(df$Score, breaks=c(6.9,7.4,7.9,8.4,8.9,9.4,10))) %>% 
  group_by(Decade, interval, .drop = FALSE) %>% 
  summarise(count=n()) -> df3

mat <- matrix(df3$count, ncol=6, byrow=T)

library(RColorBrewer)
# https://www.datanovia.com/en/blog/the-a-z-of-rcolorbrewer-palette/
barplot(mat %>% t, names.arg=unique(df3$Decade), ylim=c(0,155), col=brewer.pal(6, "Blues") )
legend(0, 150, rev(c('7+','7.5+','8+','8.5+','9+','9.5+')), 
       col=rev(brewer.pal(7, "Blues")), pch=15)
```

## Movies per Directors

Check directors with multiple movies in the list

```{r, fig.width=12, fig.height=8}
df %>% 
  count(Director, sort=TRUE) %>% 
  filter(!is.na(Director)) %>% 
  filter(n>3) -> df4

rotate_x(df4, 'n', df4$Director, 45)
```

And with movies with at least 8.75 score, ie, one of the five highest scores:

```{r, fig.width=12}
df %>% 
  filter(Score >= 8.75) %>% 
  count(Director, sort=TRUE) %>% 
  filter(!is.na(Director)) %>% 
  filter(n>2) -> df5

rotate_x(df5, 'n', df5$Director, 45)
```


## Movies per Genre



```{r}
df %>% 
  #filter(Score >= min.score) %>% 
  count(Genre) %>% 
  arrange( Genre ) -> df6

rotate_x(df6, 'n', df6$Genre, 45)
```

