---
title: "My Movies"
author: "João Neto"
date: "February 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(dplyr)
library(magrittr)
```


```{r, echo=FALSE}
df <- read.csv2('best_movies_info.csv', encoding='UTF-8')
df$Score <- as.numeric(df$Score)
df %>% 
  rename(ImdbRate = averageRating) %>% 
  rename(Votes = numVotes) %>% 
  rename(Director = primaryName) %>% 
  select(-directors) %>% 
  select(-IMDB) -> df
```

This table includes movies I think show an above than average quality in either plot, main themes and overall cinematography. This list represents around one third of all the movies I've seen and is, obviously, quite subjective :-)


```{r, warning=FALSE, echo=FALSE}
library(DT)
DT::datatable(df) 
```

## Number of Selected Movies per Year

```{r, echo=FALSE}
min.score <- 7.5
my.color <- 'steelblue'
```

Only showing movies with a minimal score of `r min.score`, given that more recent years have more lower score movies (I see more modern movies than old movies). And I still have *lots* of movies to see from the 70s and 60s.

```{r, fig.width=12, echo=FALSE}
df %>% 
  filter(Score >= min.score) %>% 
  count(Year, sort=TRUE) %>% 
  arrange( Year ) -> df2

par(mar=c(3,1,1,1))
plt <- barplot(df2$n, names.arg=df2$Year, las=2, col=my.color, ylim=c(0,max(df2$n)*1.25), yaxt="n")
text(x=plt, y=df2$n, label=df2$n, pos=3, cex=0.8, col='blue')
```

## Number of Selected Movies per Decade

Again using the same filter as above:

```{r, echo=FALSE}
df %>% 
  filter(Score >= min.score) %>% 
  count(Decade, sort=TRUE) %>% 
  arrange( Decade ) -> df2

plt <- barplot(df2$n, names.arg=df2$Decade, las=1, col=my.color, ylim=c(0,max(df2$n)*1.25), yaxt="n")
text(x=plt, y=df2$n+0.8, label=df2$n, pos=3, cex=1, col='blue')
```

## Number of Selected Movies per Country

Most movies I see are from Hollywood, but let's check how others countries are represented:

```{r, fig.width=12, fig.height=8, warning=FALSE, echo=FALSE}
df %>% 
  filter(Score >= min.score) %>% 
  filter (Country!='USA') %>% 
  count(Country, sort=TRUE) %>% 
  arrange( desc(Country) ) -> df2

par(mar=c(1,11,1,6))
plt <- barplot(df2$n, col='steelblue', horiz=TRUE, names.arg=df2$Country, 
               las=1, xlim=c(0,10+max(df2$n)), xaxt='n')
text(y=plt, x=df2$n+1.75, label=df2$n, pos = 2, cex = 0.8, col='blue')
```

## Masterpieces per Decade

Herein I define as a masterpiece a movie with a score of at least 9.5.

```{r, echo=FALSE}
rotate_x <- function(data, column_to_plot, labels_vec, rot_angle) {
  ymax <- max(data[[column_to_plot]])*1.25
  plt <- barplot(data[[column_to_plot]], col='steelblue', xaxt="n", yaxt="n", ylim=c(0,ymax))
  text(plt, par("usr")[3], labels = labels_vec, srt = rot_angle, 
       adj = c(1.1,1.1), xpd = TRUE, cex=1) 
  text(x = plt, y = data$n, label = data$n, pos = 3, cex = 1.2, col = my.color)
}

df %>% 
  filter(Score >= 9.5) %>% 
  count(Decade, sort=TRUE) %>% 
  arrange( Decade ) -> df2

rotate_x(df2, 'n', df2$Decade, 45)
```

The next plot shows how different score ranges are represented by decade,

```{r, fig.width=10, warning=FALSE, echo=FALSE}
df %>% 
  mutate(interval = cut(df$Score, breaks=c(6.9,7.4,7.9,8.4,8.9,9.4,10))) %>% 
  group_by(Decade, interval, .drop = FALSE) %>% 
  summarise(count=n()) -> df3

mat <- matrix(df3$count, ncol=6, byrow=T)

library(RColorBrewer)
# https://www.datanovia.com/en/blog/the-a-z-of-rcolorbrewer-palette/
barplot(mat %>% t, names.arg=unique(df3$Decade), ylim=c(0,155), col=brewer.pal(6, "Blues") )
legend(0, 150, rev(c('7+','7.5+','8+','8.5+','9+','9.5+')), 
       col=rev(brewer.pal(7, "Blues")), pch=15)
```

## Movies per Directors

Let's check directors with multiple movies in the list,

```{r, fig.width=12, fig.height=8, echo=FALSE}
df %>% 
  count(Director, sort=TRUE) %>% 
  filter(!is.na(Director)) %>% 
  filter(n>4) -> df4

par(mar=c(1,11,1,6))
plt <- barplot(df4$n, col='steelblue', horiz=TRUE, names.arg=df4$Director, 
               las=1, xlim=c(0,10+max(df4$n)), xaxt='n')
text(y=plt, x=df4$n+0.8, label=df4$n, pos = 2, cex = 0.8, col='blue')
```

Directors with movies with a score of at least 8.5,

```{r, fig.width=12, fig.height=6, echo=FALSE}
df %>% 
  filter(Score >= 8.5) %>% 
  count(Director, sort=TRUE) %>% 
  filter(!is.na(Director)) %>% 
  filter(n>2) -> df5

par(mar=c(1,11,1,1))
plt <- barplot(df5$n, col='steelblue', horiz=TRUE, names.arg=df5$Director, 
               las=1, xlim=c(0,10+max(df5$n)), xaxt='n')
text(y=plt, x=df5$n+0.5, label=df5$n, pos = 2, cex = 0.8, col='blue')
```

And finally who made the masterpieces (>=9.5),

```{r, fig.width=12, fig.height=6, echo=FALSE}
df %>% 
  filter(Score >= 9.5) %>% 
  count(Director, sort=TRUE) %>% 
  filter(!is.na(Director)) -> df5

par(mar=c(1,11,1,1))
plt <- barplot(df5$n, col='steelblue', horiz=TRUE, names.arg=df5$Director, 
               las=1, xlim=c(0,10+max(df5$n)), xaxt='n')
text(y=plt, x=df5$n+0.5, label=df5$n, pos = 2, cex = 0.8, col='blue')
```

## Movies per Genre

```{r, fig.width=12, fig.height=6, echo=FALSE}
df %>% 
  #filter(Score >= min.score) %>% 
  count(Genre) %>% 
  arrange( desc(Genre) ) -> df6

par(mar=c(1,11,1,1))
plt <- barplot(df6$n, col='steelblue', horiz=TRUE, names.arg=df6$Genre, 
               las=1, xlim=c(0,20+max(df6$n)), xaxt='n')
text(y=plt, x=df6$n+7, label=df6$n, pos = 2, cex = 0.8, col='blue')
```

