---
title: "My Movies"
author: "João Neto"
date: "February -- December, 2021"
output: html_document
---

<!--  To run shiny server place this above
runtime: shiny 
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(dplyr)
library(magrittr)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
df <- read.csv2('best_movies_info.csv', encoding='UTF-8')
df$Score <- as.numeric(df$Score)
df$link <- paste0('<a href="https://www.imdb.com/title/', df$IMDB, '" target="_blank">imdb</a>')
df %>% 
  rename(Rate = Score) %>% 
  rename(Director = primaryName) %>% 
  select(-directors) ->df 

### read imdb table

## we'll get imdb rate, movie time and popular votes from IMDB database

df.imdb <- read.csv('imdb-ratings.csv', encoding='UTF-8')
df.imdb %>% 
  rename(IMDB = Const) %>% 
  rename(Time = "Runtime..mins.") %>% 
  rename(Imdb = IMDb.Rating) %>% 
  rename(Votes = Num.Votes) %>% 
  select(-Your.Rating) %>% 
  select(-Date.Rated) %>% 
  select(-Title) %>% 
  select(-URL) %>% 
  select(-Genres) %>% 
  select(-Year) %>% 
  select(-Release.Date) %>% 
  select(-Directors) %>% 
  select(-Title.Type) -> df.imdb2

### Join Tables

df.join <- left_join(df, df.imdb2, by=c("IMDB"="IMDB"))
df.join %>% 
  select(-IMDB) %>% 
  select(Title,Year,Decade,Country,Genre,Time,Rate,Imdb,Votes,Director,link) -> df
```

This table includes movies I think show an above than average quality in either plot, main themes and overall cinematography. This list represents around 45% of [all the movies I've seen](https://www.imdb.com/user/ur3443219/ratings?ref_=nv_usr_rt_4) and is, obviously, quite subjective :-)

```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(DT)
DT::datatable(df, escape=FALSE) 
```

## Number of Selected Movies per Year

```{r, echo=FALSE}
min.score <- 7
my.color <- 'steelblue'
```

Showing movies with a minimal rating of `r min.score`. The list of movies I wanted to see from 1970-2019 is (somewhat) complete. 

```{r, fig.width=12, echo=FALSE, eval=TRUE}
df %>% 
  filter(Rate >= min.score) %>% 
  count(Year, sort=TRUE) %>% 
  filter(Year >= 1970) %>%
  arrange( Year ) -> df2

par(mar=c(3,1,1,1))
plt <- barplot(df2$n, names.arg=df2$Year, las=2, col=my.color, ylim=c(0,max(df2$n)*1.25), yaxt="n")
text(x=plt, y=df2$n, label=df2$n, pos=3, cex=0.8, col='blue')
```


There are hundreds to see from the 1920s to the 1960s, and these are the respective wish-lists:

+ [wishlist from the 1920s](https://www.imdb.com/list/ls088146253/?pf_rd_m=A2FGELUUNOQJNL&pf_rd_p=4dc7ad1a-76a6-49eb-9acb-5d6959572df8&pf_rd_r=2N4WWMA2RBEP12AVJGS9&pf_rd_s=right-4&pf_rd_t=48201&pf_rd_i=watchlist&ref_=wt_otl_1)

+ [wishlist from the 1930s](https://www.imdb.com/list/ls088107424/?pf_rd_m=A2FGELUUNOQJNL&pf_rd_p=4dc7ad1a-76a6-49eb-9acb-5d6959572df8&pf_rd_r=GJR77FD60TS77BB3BTM4&pf_rd_s=right-4&pf_rd_t=48201&pf_rd_i=watchlist&ref_=wt_otl_2)


+ [wishlist from the 1940s](https://www.imdb.com/list/ls088795556/?pf_rd_m=A2FGELUUNOQJNL&pf_rd_p=4dc7ad1a-76a6-49eb-9acb-5d6959572df8&pf_rd_r=0FCARTR5AZ8DRVB27SH3&pf_rd_s=right-4&pf_rd_t=48201&pf_rd_i=watchlist&ref_=wt_otl_4)


+ [wishlist from the 1950s](https://www.imdb.com/list/ls089830524/?pf_rd_m=A2FGELUUNOQJNL&pf_rd_p=4dc7ad1a-76a6-49eb-9acb-5d6959572df8&pf_rd_r=G8MGE7R65T5SR6M8362N&pf_rd_s=right-4&pf_rd_t=48201&pf_rd_i=watchlist&ref_=ttls_vw_grd&sort=list_order,asc&st_dt=&mode=grid&page=1)

+ [wishlist from the 1960s](https://www.imdb.com/list/ls089835133/?pf_rd_m=A2FGELUUNOQJNL&pf_rd_p=4dc7ad1a-76a6-49eb-9acb-5d6959572df8&pf_rd_r=E1XAD5HDMTDS4WJ8NJPH&pf_rd_s=right-4&pf_rd_t=48201&pf_rd_i=watchlist&ref_=ttls_vw_grd&sort=list_order,asc&st_dt=&mode=grid&page=1)

```{r, fig.width=12, echo=FALSE, eval=TRUE}
df %>% 
  filter(Rate >= min.score) %>% 
  count(Year, sort=TRUE) %>% 
  filter(Year < 1970) %>%
  arrange( Year ) -> df2

par(mar=c(3,1,1,1))
plt <- barplot(df2$n, names.arg=df2$Year, las=2, col=my.color, ylim=c(0,max(df2$n)*1.25), yaxt="n")
text(x=plt, y=df2$n, label=df2$n, pos=3, cex=0.8, col='blue')
```

```{r, echo=FALSE, eval=FALSE}
inputPanel(
  sliderInput("score", label="minimum movie score", 
              min=7, max=10, value=7.5, step=0.25)
)

output$g1 <- renderPlot({
  df %>% 
  filter(Rate >= input$score) %>% 
  count(Year, sort=TRUE) %>% 
  arrange( Year ) -> df2

  par(mar=c(3,1,1,1))
  plt <- barplot(df2$n, names.arg=df2$Year, las=2, col=my.color,
                 ylim=c(0,max(df2$n)*1.25), yaxt="n")
  text(x=plt, y=df2$n, label=df2$n, pos=3, cex=0.8, col='blue')
})

plotOutput("g1", height="400px")
br()
```




```{r, echo=FALSE, eval=TRUE}
rotate_x <- function(data, column_to_plot, labels_vec, rot_angle) {
  ymax <- max(data[[column_to_plot]])*1.25
  plt <- barplot(data[[column_to_plot]], col='steelblue', xaxt="n", yaxt="n", ylim=c(0,ymax))
  text(plt, par("usr")[3], labels = labels_vec, srt = rot_angle, 
       adj = c(1.1,1.1), xpd = TRUE, cex=1) 
  text(x = plt, y = data$n, label = data$n, pos = 3, cex = 1.2, col = my.color)
}
```

## Totality of Movies ranked

These numbers include all movies that I ranked at IMDB:

```{r, fig.width=6, fig.height=3, echo=FALSE, eval=TRUE}
df.imdb %>% 
  mutate(Decade = floor(Year/10)*10) %>% 
  count(Decade) %>% 
  arrange(Decade) -> df2

par(mar = c(2.5, .5, .5, .5))
rotate_x(df2, 'n', df2$Decade, 45)
```

## Number of Selected Movies per Decade

Using a minimal score of 7, to include only the movies at the initial table:

```{r, fig.width=6, fig.height=3, echo=FALSE, eval=TRUE}
df %>% 
  filter(Rate >= min.score) %>% 
  count(Decade, sort=TRUE) %>% 
  arrange( Decade ) -> df2

par(mar = c(2.5, .5, .5, .5))
rotate_x(df2, 'n', df2$Decade, 45)
# plt <- barplot(df2$n, names.arg=df2$Decade, las=1, col=my.color, ylim=c(0,max(df2$n)*1.25), yaxt="n")
# text(x=plt, y=df2$n+0.8, label=df2$n, pos=3, cex=1, col=my.color)
```

```{r, echo=FALSE, eval=FALSE}
inputPanel(
  sliderInput("score2", label="minimum movie score", 
              min=7, max=10, value=7.5, step=0.25)
)

output$g2 <- renderPlot({
df %>% 
  filter(Rate >= input$score2) %>% 
  count(Decade, sort=TRUE) %>% 
  arrange( Decade ) -> df2

  plt <- barplot(df2$n, names.arg=df2$Decade, las=1, col=my.color,
                 ylim=c(0,max(df2$n)*1.25), yaxt="n")
  text(x=plt, y=df2$n+0.8, label=df2$n, pos=3, cex=1, col='blue')
})

plotOutput("g2", height="400px")
br()
```

## Movie quality per Decade

Let's see how many very good films (rating at least 8) each decade produced,

```{r, fig.width=6, fig.height=3, echo=FALSE}
df %>% 
  filter(Rate >= 8) %>% 
  count(Decade, sort=TRUE) %>% 
  arrange( Decade ) -> df2

par(mar = c(2.5, .5, .5, .5))
rotate_x(df2, 'n', df2$Decade, 45)
```

And how many great films (rating at least 9) each decade produced,

```{r, fig.width=6, fig.height=3, echo=FALSE}
df %>% 
  filter(Rate >= 9) %>% 
  count(Decade, sort=TRUE) %>% 
  arrange( Decade ) -> df2

par(mar = c(2.5, .5, .5, .5))
rotate_x(df2, 'n', df2$Decade, 45)
```

And masterpieces (rating of at least 9.5) per decade,

```{r, fig.width=6, fig.height=3, echo=FALSE}
df %>% 
  filter(Rate >= 9.5) %>% 
  count(Decade, sort=TRUE) %>% 
  arrange( Decade ) -> df2

par(mar = c(2.5, .5, .5, .5))
rotate_x(df2, 'n', df2$Decade, 45)
```

The next plot shows how different rating ranges are represented by decade,

```{r, fig.width=8, fig.height=6, warning=FALSE, echo=FALSE}
df %>% 
  mutate(interval = cut(df$Rate, breaks=c(6.9,7.4,7.9,8.4,8.9,9.4,10))) %>% 
  group_by(Decade, interval, .drop = FALSE) %>% 
  summarise(count=n()) -> df3

mat <- matrix(df3$count, ncol=6, byrow=T)

library(RColorBrewer)
par(mar = c(2.5, 2.5, 1.5, 1.5))
# https://www.datanovia.com/en/blog/the-a-z-of-rcolorbrewer-palette/
barplot(mat %>% t, names.arg=unique(df3$Decade), ylim=c(0,250), col=brewer.pal(6, "Blues") )
legend(.25, 180, rev(c('7+','7.5+','8+','8.5+','9+','9.5+')), 
       col=rev(brewer.pal(7, "Blues")), pch=15)
```

## Movies per Directors

Let's check directors with multiple movies in the list,

```{r, fig.width=14, fig.height=12, echo=FALSE}
df %>% 
  count(Director, sort=TRUE) %>% 
  filter(!is.na(Director)) %>% 
  filter(n>4) -> df4

par(mar=c(1,11,1,6))
plt <- barplot(df4$n, col='steelblue', horiz=TRUE, names.arg=df4$Director, 
               las=1, xlim=c(0,10+max(df4$n)), xaxt='n')
text(y=plt, x=df4$n+0.8, label=df4$n, pos = 2, cex = 0.8, col='blue')
```

Directors with movies with a rating of at least 8.5,

```{r, fig.width=12, fig.height=6, echo=FALSE}
df %>% 
  filter(Rate >= 8.5) %>% 
  count(Director, sort=TRUE) %>% 
  filter(!is.na(Director)) %>% 
  filter(n>2) -> df5

par(mar=c(1,11,1,1))
plt <- barplot(df5$n, col='steelblue', horiz=TRUE, names.arg=df5$Director, 
               las=1, xlim=c(0,10+max(df5$n)), xaxt='n')
text(y=plt, x=df5$n+0.4, label=df5$n, pos = 2, cex = 0.8, col='blue')
```

And finally who made the masterpieces (>=9.5),

```{r, fig.width=12, fig.height=6, echo=FALSE}
df %>% 
  filter(Rate >= 9.5) %>% 
  count(Director, sort=TRUE) %>% 
  filter(!is.na(Director)) -> df5

par(mar=c(1,11,1,1))
plt <- barplot(df5$n, col='steelblue', horiz=TRUE, names.arg=df5$Director, 
               las=1, xlim=c(0,10+max(df5$n)), xaxt='n')
text(y=plt, x=df5$n+0.4, label=df5$n, pos = 2, cex = 0.8, col='blue')
```

The next table sums, for each director, the scores of each film rated here. A film ranked 7 gets 1 point, 7.25 gets 2 points, upto a score 10 that gets 13 points. For the Imdb score, films with score less or equal to 6.5 get negative points.

```{r, echo=FALSE}
# a 7 receives 1 point, a 10 receives 13 points
score <- function(rate) {
  rate*4-27
}

director.score <- function(rates) {
  round(sum(as.numeric(Map(score, rates))),2)
}

df %>% 
  group_by(Director) %>% 
  summarize(Score = director.score(Rate)) -> directors

df %>% 
  group_by(Director) %>% 
  summarize(Score.Imdb = director.score(Imdb)) -> directors2

directors$Imdb <- directors2$Score.Imdb

directors %>% 
  arrange(desc(Score)) -> directors

DT::datatable(directors, escape=FALSE) 
```
The next table show these scores per decade and director.

```{r, echo=FALSE}
df %>% 
  group_by(Director, Decade) %>% 
  summarize(Score = director.score(Rate)) -> directors

df %>% 
  group_by(Director, Decade) %>% 
  summarize(Score.Imdb = director.score(Imdb)) -> directors2

directors$Imdb <- directors2$Score.Imdb

directors %>% 
  arrange(desc(Score)) -> directors

DT::datatable(directors, escape=FALSE) 
```

## Movies per Genre

```{r, fig.width=12, fig.height=6, echo=FALSE}
df %>% 
  #filter(Score >= min.score) %>% 
  count(Genre) %>% 
  arrange( desc(Genre) ) -> df6

par(mar=c(1,11,1,1))
plt <- barplot(df6$n, col='steelblue', horiz=TRUE, names.arg=df6$Genre, 
               las=1, xlim=c(0,20+max(df6$n)), xaxt='n')
text(y=plt, x=df6$n+12, label=df6$n, pos=2, cex=0.8, col='blue')
```

## Movies per Country

Most movies I see are from Hollywood, but let's check how others countries are represented:

```{r, fig.width=12, fig.height=8, warning=FALSE, echo=FALSE}
df %>% 
  filter(Rate >= 7) %>% 
  filter (Country!='USA') %>% 
  count(Country, sort=TRUE) %>% 
  arrange( desc(Country) ) -> df2

par(mar=c(1,11,1,6))
plt <- barplot(df2$n, col='steelblue', horiz=TRUE, names.arg=df2$Country, 
               las=1, xlim=c(0,10+max(df2$n)), xaxt='n')
text(y=plt, x=df2$n+4, label=df2$n, pos = 2, cex = 0.8, col='blue')
```



```{r, fig.width=12, fig.height=8, echo=FALSE, eval=FALSE}
df %>% 
  filter(Rate >= 9) %>% 
  count(Country, sort=TRUE)  -> df2

par(mar=c(1,11,1,6))
plt <- barplot(df2$n, col='steelblue', horiz=TRUE, names.arg=df2$Country, 
               las=1, xlim=c(0,10+max(df2$n)), xaxt='n')
text(y=plt, x=df2$n+4, label=df2$n, pos = 2, cex = 0.8, col='blue')
```



```{r, echo=FALSE, eval=FALSE}
plot(df$Year, df$Rate, pch=20, col='lightgrey')
fit <- lm(Rate ~ Year, df)
abline(fit, col='blue')
```




